Confronting Wicked Crypto

### 2021-02-23 articles/tots-ieee/Article.tex
Update TOPS ACM article, copy in chapter 6
changed author format to match journal requirements. Added placeholders for author biographies

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SETUP %
\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

@@

%%%%%%%%%%% Commands
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\tt#1{\mbox{\texttt{#1}}}

\newcommand*{\thead}[1]{\multicolumn{1}{c}{\bfseries #1}}

%% Mine
\def\tt#1{\mbox{\texttt{#1}}}
\def\bb#1{\mbox{\textbf{#1}}}
\def\ii#1{\mbox{\textit{#1}}}
\newcommand{\myfig}[1]{Figure~\ref{#1}}
\newcommand{\mysec}[1]{Section~\ref{#1}}

@@

\author{\IEEEauthorblockN{Kevin Kredit}
\IEEEauthorblockA{\textit{GVSU ACS Department} \\
Grand Rapids, Michigan \\
Email: k.kredit.us@ieee.org}
\and
% FIXME: Prof. Kalafut, update as appropriate
% Is there a way to indicate that you are faculty and I am not? Label yourself with PhD, perhaps?
\IEEEauthorblockN{Andrew Kalafut, Ph.D.}
\IEEEauthorblockA{\textit{GVSU ACS Department} \\
Grand Rapids, Michigan \\
Email: kalafuta@gvsu.edu}
}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SETUP %
\documentclass{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

@@

%%%%%%%%%%% Commands
\def\tt#1{\mbox{\texttt{#1}}}
\def\bb#1{\mbox{\textbf{#1}}}
\def\ii#1{\mbox{\textit{#1}}}
\newcommand{\myfig}[1]{Figure~\ref{#1}}
\newcommand{\mysec}[1]{Section~\ref{#1}}

@@

\author{Kevin Kredit and Andrew Kalafut\thanks{K. Kredit was with Grand Valley State University. A. Kalafut is with Grand Valley State University}}

%\IEEEauthorblockN{Kevin Kredit}
%\IEEEauthorblockA{\textit{GVSU ACS Department} \\
%Grand Rapids, Michigan \\
%Email: k.kredit.us@ieee.org}
%\and
% FIXME: Prof. Kalafut, update as appropriate
% Is there a way to indicate that you are faculty and I am not? Label yourself with PhD, perhaps?
%\IEEEauthorblockN{Andrew Kalafut, Ph.D.}
%\IEEEauthorblockA{\textit{GVSU ACS Department} \\
%Grand Rapids, Michigan \\
%Email: kalafuta@gvsu.edu}
%}

@@

\begin{IEEEbiography}{Kevin Kredit}
  Placeholder biography for Kevin. Please fill in.
\end{IEEEbiography}

\begin{IEEEbiography}{Andrew Kalafut}
  Placeholder biography for prof. kalafut. Will fill in later 
\end{IEEEbiography}
